Sexual selection improves fitness: a meta-analysis

### 2018-06-06 meta_analysis_sexual_selection_pop_fitness.Rmd
6/6 Update

---
title: 'Effects of sexual selection on non-sexual fitness components: a meta-analysis'
author: "Justin G. Cally^1^, Luke Holman^1^, Devi Stuart-Fox^1^ <br></br> <br></br> ^1^The University of Melbourne"
subtitle: Supplementary Material
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
  pdf_document: default
---

@@

Here we show the residual effect sizes for each outcome measured. The following forest plot is based on the residual effect sizes. The model is an intercept only model with standard random effects structure.

>>>>

---
title: 'Sexual selection improves fitness: a meta-analysis'
author: "Justin G. Cally^1^, Luke Holman^1^, Devi Stuart-Fox^1^ <br></br> <br></br> ^1^The University of Melbourne"
subtitle: Supplementary Material
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
  pdf_document: default
---

@@

Here we show the raw effect sizes for each fitness component measured.
